A Cost-based Approach for Fast Intrusion Detection

### 2017-06-04 tex/paper_v1.tex
train example

\section{Related Work}\label{sec:relatedwork}
\subsection{Detection Methodology}
\subsection{Machine Learning for Intrusion Detection}
\subsection{Public Datasets}\label{sec:publicdatasets}

@@

\section{Future Work}\label{sec:futurework}

>>>>

\section{Related Work}\label{sec:relatedwork}
\subsection{Detection Methodology}

\subsection{Machine Learning for Intrusion Detection}

\subsection{Public Datasets}\label{sec:publicdatasets}

@@

\section{Future Work}\label{sec:futurework}
As mentioned in Sec \ref{sec:experiment}, due to the coming deadline, some of the experiments are not completely finished.

The future work for this paper is listed as follows:
\begin{itemize}
\item Calculate the average performance for all the models, not for only some examples.
\item Measure the specific improvement made by distinguishing different level of features quantitatively, such as calculate the exact cost saved for detecting some packets.
\end{itemize}

There are also some practical need to be solved for further implementation:
\begin{itemize}
\item There are some protocol type and service with very few training data, such as TCP pm\_dump, UDP tftp\_u and ICMP urh\_i etc. This issue will make it impossible to train a neural network model. Maybe some signature-based technique are needed here.
\item It will cost too much time to train and tune parameters for every model, specifically $72$ models in NSL-KDD dataset. But currently I just train the example models manually.
\end{itemize}
